---
title: "PCRSimPlot"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PCRSimPlot

<!-- badges: start -->
<!-- badges: end -->

PCRSimPlot is an R package for simulating and plotting PCR (Polymerase Chain Reaction) data. The package includes functions for generating PCR data based on specified parameters and visualizing the results.


## Installation

You can install the development version of PCRSimPlot like so:

``` r
You can install the development version of **PCRSimulation** from GitHub using the `devtools` package:

```r
# Install devtools if you haven't already
# install.packages("devtools")

# Install PCRSimPlot
devtools::install_github("AttaLowe/PCRSimPlot")

# Functions
`simulate_pcr()`
Simulates PCR data based on initial DNA concentration, amplification efficiency, and a fluorescence threshold.

# Usage
```r
simulate_pcr(N0, E, threshold = 10000)

```r
Arguments:

N0: Initial DNA concentration (numeric). For example, 10.
E: Amplification efficiency (numeric, between 1 and 2). For example, 1.8.
threshold: Fluorescence threshold for detecting the PCR signal (numeric, default is 10000).
Returns:

A list with two components:

pcr_data: A data frame containing the simulated PCR data with columns Cycle, DNA, and Fluorescence.
Ct: The cycle threshold (Ct) value at which the fluorescence exceeds the threshold.

```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example1}
library(PCRSimPlot)
result <- simulate_pcr(N0 = 10, E = 1.8)
print(result$pcr_data)
print(result$Ct)

```
```
`plot_pcr()`
Plots the simulated PCR data, showing fluorescence over cycles and the cycle threshold (Ct).
# Usage
```r
plot_pcr(pcr_data, Ct)
```r
Arguments:

pcr_data: A data frame containing the PCR data (typically from simulate_pcr()).
Ct: The cycle threshold (Ct) value.
Returns:

A ggplot object visualizing the PCR data with a line plot of fluorescence over cycles, including a vertical line indicating the Ct valu

```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example2}

result <- simulate_pcr(N0 = 10, E = 1.8)
plot <- plot_pcr(result$pcr_data, result$Ct)
print(plot)

```
```
# Example
Here’s a full example of how to use the package:
```{r example3, message=TRUE}
# Load the package
library(PCRSimPlot)

# Simulate PCR data
result <- simulate_pcr(N0 = 10, E = 1.8)

# Print the simulated data and Ct value
print(result$pcr_data)
print(result$Ct)

# Plot the results
plot <- plot_pcr(result$pcr_data, result$Ct)
print(plot)
```
























