---
title: "PCRSimPlot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PCRSimPlot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PCRSimPlot)
```

## Introduction

The PCRSimPlot package provides functions to simulate and plot PCR (Polymerase Chain Reaction) data. This vignette demonstrates how to use the simulate_pcr() and plot_pcr() functions to generate and visualize PCR data.

## Simulate PCR Data

Use the simulate_pcr() function to generate simulated PCR data. This function requires initial DNA concentration (N0), amplification efficiency (E), and an optional fluorescence threshold.

```{r}
result <- simulate_pcr(N0 = 10, E = 1.8)

```

The simulate_pcr() function returns a list with two components: pcr_data (a data frame of simulated PCR data) and Ct (the cycle threshold value).

```{r}
print(result$pcr_data)
print(result$Ct)

```

## Plot PCR Data

Use the plot_pcr() function to visualize the simulated PCR data. This function creates a ggplot object showing fluorescence over cycles, with a vertical line indicating the cycle threshold (Ct).

```{r}
plot <- plot_pcr(result$pcr_data, result$Ct)
print(plot)

```

## Conclusion

The PCRSimPlot package provides an easy way to simulate and visualize PCR data. Use the provided functions to gain insights into PCR dynamics and results.



